\chapter{Simulator}
The simulator objective is to have a instrument to validate our ides and results. In particoular we want obtain sperimentally for each task, the distribution of job execution time.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Taskset Model}
\label{sec:task_model}
In this section we define the taskset model, i.e., how the tasks in the taskset can be define and which are their non functional charatteristics.
From now on we suppose that:
\begin{itemize}
    \item Each task is indipendent from the others. This means that there aren't shared resources among two tasks.
    \item Each task have a single elementary execution unit, i.e. each task have only one chunk.
    \item The task execution time is defined probabilistically, i.e. the the execution time of each time is sampled from some distribution; this includes also the deterministic one.
    \item The jobs execution time are i.i.d. (i.e., indipendent and identically distributed). This means that only one distribution that represents the job execution time pattern of a given task. Maybe at the end we will move towards a model in ehich we can define a reletion between job execution time.
    \item Task can be both periodic and sporadic (i.e. the releases between two consecutive job of the same task are separated from a minimum inter-arrival time). This releasing time is defined in a probabilistic way by some distribution.
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Input and Output}
The simulator input are the following:
\begin{itemize}
    \item A fixed priority scheduling algorithm.
    \item The taskset caratterized from the assumptions in Section~\ref{sec:task_model}.
    \item The duration of the simulation.
\end{itemize}

\myskip

The outputs are the Cumulative Distribution Function (CDF) and teh Probability Density Function (PDF) of the job execution time distribution for each task.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Implementation}